\documentclass[12pt]{article}%
\usepackage{graphics, graphicx, cite, fancybox, setspace}
\usepackage{color}
\usepackage{boxedminipage}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{url}
\usepackage{wrapfig,sectsty}
\usepackage[letterpaper, left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{multirow}
\usepackage{times}
\usepackage{verbatim}
\usepackage{epsfig}
\usepackage{subcaption}

%
\usepackage{array}
\usepackage{rotating}


\usepackage{enumitem}
\usepackage{float}
\usepackage{titlesec}







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\titleformat{\section}
  {\normalfont\fontsize{14}{1em}\bfseries}{\thesection}{1em}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\bi{\begin{itemize}     % Begin Itemize
\vspace{-0.5em}\setlength\itemsep{0em}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
{\LARGE 05/13/19 Weekly Report}\\
\vspace{0.5em}
{\Large Hunter Kippen}
\vspace{0.5em}
\end{center}


\section{What I worked on last week}
\bi
\item I wrote drafts for the problem formulation and proposed solution sections of my Thesis.
\item I finished generating the necessary data to run all experiments necessary for the Thesis. This means fixed amounts of deletion for all camera models. If we want to add more experiments with variable numbers of frames deleted, I will need a few days to create the data.
\end{itemize}

\section{Problems I encountered}
\bi
\item I found that I did not generate MPEG-2 like traces for all videos in my dataset. I went back and started creating this data this past weekend, but it will not be complete until tomorrow as per my estimates. As such I could not complete a draft of my experimental results section by today as I had hoped.
\end{itemize}

\section{What I plan to do this week}
\bi
\item I will write the drafts for the rest of my sections for my thesis. I should be able to finish in time by next Tuesday as required. I will need some guidance as to what I should put into my background and experimental sections.
\item I will talk to Sean and see if I can get a small extension (day or two) to get more revisions of existing sections in place.
\end{itemize}


% Bib/refs go here if used

\begin{comment}
\pagebreak
%\bibliographystyle{plain}
\bibliographystyle{myIEEE}
\bibliography{StammRefs}
%\bibliography{StammRefs,kandasamy_v2,kandasamy}
\end{comment}


\end{document} 