\documentclass[12pt]{article}%
\usepackage{graphics, graphicx, cite, fancybox, setspace}
\usepackage{color}
\usepackage{boxedminipage}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{url}
\usepackage{wrapfig,sectsty}
\usepackage[letterpaper, left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{multirow}
\usepackage{times}
\usepackage{verbatim}
\usepackage{epsfig}
\usepackage{subcaption}

%
\usepackage{array}
\usepackage{rotating}


\usepackage{enumitem}
\usepackage{float}
\usepackage{titlesec}







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\titleformat{\section}
  {\normalfont\fontsize{14}{1em}\bfseries}{\thesection}{1em}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\bi{\begin{itemize}     % Begin Itemize
\vspace{-0.5em}\setlength\itemsep{0em}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
{\LARGE 12/03/18 Weekly Report}\\
\vspace{0.5em}
{\Large Hunter Kippen}
\vspace{0.5em}
\end{center}


\section{What I worked on last week}
\bi
\item I ostensibly created a working method for running the diamond search based block matching algorithm using Dr. Shackleford's Cython modules.
\item I attempted to run my program on my video dataset, but...
\end{itemize}



\section{Problems I encountered}
\bi
\item I was getting a myriad of configuration issues, which I solved.
\item However, I am still getting an issue with python and numpy version incompatibilities which
is preventing me from completing my experiments.
\end{itemize}

\section{What I plan to do this week}
\bi
\item I plan on fixing these issues (Owen says that it worked for him using the Anaconda python
framework, so I will be attempting to use that for development purposes.
\item Once I get everything up and running, I am planning to make a few test images to see if the block matching works correctly. I will also run the algorithm on multiple videos with easily estimatable motion for sanity checking, and will compare against Dr Shackleford's own tools.
\item After fixing any algorithmic errors, I will finish my script to compute the predicted frame and the prediction error sequence.
\item Time permitting, I will also run this on my dataset, generating ROC curves and the like for my data.
\end{itemize}


% Bib/refs go here if used

\begin{comment}
\pagebreak
%\bibliographystyle{plain}
\bibliographystyle{myIEEE}
\bibliography{StammRefs}
%\bibliography{StammRefs,kandasamy_v2,kandasamy}
\end{comment}


\end{document} 