\documentclass[12pt]{article}%
\usepackage{graphics, graphicx, cite, fancybox, setspace}
\usepackage{color}
\usepackage{boxedminipage}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{url}
\usepackage{wrapfig,subfigure,sectsty}
\usepackage[letterpaper, left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{multirow}
\usepackage{times}
\usepackage{verbatim}
\usepackage{epsfig}
%
\usepackage{array}
\usepackage{rotating}


\usepackage{enumitem}
\usepackage{float}
\usepackage{titlesec}







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\titleformat{\section}
  {\normalfont\fontsize{14}{1em}\bfseries}{\thesection}{1em}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\bi{\begin{itemize}     % Begin Itemize
\vspace{-0.5em}\setlength\itemsep{0em}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
{\LARGE 10/15/18 Weekly Report}\\
\vspace{0.5em}
{\Large Hunter Kippen}
\vspace{0.5em}
\end{center}


\section{What I worked on last week}
\bi
\item I wrote the program for Generating frame deleted videos. Currently it exists as three functions. One function takes a video and dumps the frames to a specified directory, while a second takes video frames from the dump function and reencodes them into a video. The third function takes in a video to be decoded, start and end frames, and the output file path, and creates the frame deleted video.
\item I started 
\end{itemize}


\section{Problems I encountered}
\bi
\item I got pretty sick last week, and was unable to make significant progress on actually using FFMPEG on our video data. This is because I had around 36 hours of homework to do between last Thursday and Today. 
\end{itemize}

\section{What I plan to do this week}
\bi
\item This week I plan of figuring out how to use FFMPEG to automatically delete frames from a video and reencode them. If I complete this, I will then write a bash script to run FFMPEG on a couple of camera models to create a small data set.
\item If time permits (I still have to make up a lot of homework, and study for midterms next week), I will also delve into h.264 poker's python interface and write a function that outputs the p-frame prediction error sequence to a text or csv type file.
\end{itemize}




% Bib/refs go here if used

\begin{comment}
\pagebreak
%\bibliographystyle{plain}
\bibliographystyle{myIEEE}
\bibliography{StammRefs}
%\bibliography{StammRefs,kandasamy_v2,kandasamy}
\end{comment}


\end{document} 