\documentclass[12pt]{article}%
\usepackage{graphics, graphicx, cite, fancybox, setspace}
\usepackage{color}
\usepackage{boxedminipage}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{url}
\usepackage{wrapfig,sectsty}
\usepackage[letterpaper, left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{multirow}
\usepackage{times}
\usepackage{verbatim}
\usepackage{epsfig}
\usepackage{subcaption}

%
\usepackage{array}
\usepackage{rotating}


\usepackage{enumitem}
\usepackage{float}
\usepackage{titlesec}







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\titleformat{\section}
  {\normalfont\fontsize{14}{1em}\bfseries}{\thesection}{1em}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\bi{\begin{itemize}     % Begin Itemize
\vspace{-0.5em}\setlength\itemsep{0em}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
{\LARGE 04/29/19 Weekly Report}\\
\vspace{0.5em}
{\Large Hunter Kippen}
\vspace{0.5em}
\end{center}


\section{What I worked on last week}
\bi
\item I wrote an outline for my thesis. I am not entirely sure if it is detailed enough, but I believe I covered a minimally sufficient amount of information to complete the thesis.
\item I started making more data. I am going through camera models with GOPs with only I and P frames. Most Samsung and a few other devices have this property, so I will start experiments with those devices.
\end{itemize}

\section{Problems I encountered}
\bi
\item There are no problems that I had last week. Things seem to be moving in a good direction.
\end{itemize}

\section{What I plan to do this week}
\bi
\item I will tweak my prediction error extractor code to skip B-frames, so that our entire dataset is available to use.
\item I will update my frame deletion software to allow for it to properly match video M and N values (GOP structure) and support randomization. These tweaks are small and should only take a few hours at the most.
\item I will begin writing the problem formulation section of the thesis, as I believe this will be the hardest one for me to get right. As such, I need to start it as early as possible.
\end{itemize}


% Bib/refs go here if used

\begin{comment}
\pagebreak
%\bibliographystyle{plain}
\bibliographystyle{myIEEE}
\bibliography{StammRefs}
%\bibliography{StammRefs,kandasamy_v2,kandasamy}
\end{comment}


\end{document} 