%%
%% This is file `example.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% drexel-thesis.dtx  (with options: `example')
%% 
%% This is a generated file.
%% 
%% Copyright (C) 2010 W. Trevor King
%% 
%% This file may be distributed and/or modified under the conditions of
%% the LaTeX Project Public License, either version 1.3 of this license
%% or (at your option) any later version.  The latest version of this
%% license is in:
%% 
%%    http://www.latex-project.org/lppl.txt
%% 
%% and version 1.3 or later is part of all distributions of LaTeX version
%% 2003/06/01 or later.
%% 
%% See drexel-thesis.pdf for details.
\documentclass[subfig,blackref,approvalform]{drexel-thesis}

%% Enter the appropriate information here
\author{Hunter Kippen}
\title{New Methods for Detecting Frame Deletion in Modern Video}
\DUTmonth{May}
\DUTyear{2019}
\degree{Master of Science}
\advisor{Dr. Matthew Stamm, Ph.D.}
\copyrighttext{\copyrighttextCCBYSA}

%\usepackage[super,sort&compress]{natbib} % fancy citation extensions
%\bibliographystyle{IEEE}

\usepackage[backend=bibtex,style=ieee,natbib=true]{biblatex}
\addbibresource{references.bib}

\usepackage{fancyvrb} % nicer verbatim handling
\DefineShortVerb{\|}  % \verb+TEXT+  ->  |TEXT|

\renewenvironment{preamble}{% look, we're clobbering an environment!
  What preamble?\begingroup\color{white}}{\endgroup}

\usepackage[english]{babel} % English blindtext
\usepackage{blindtext} % macros for producing dummy output
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{bm}
\usepackage{subfig}
\usepackage{wrapfig}
\usepackage{tabu}
\usepackage{adjustbox}

\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\R}{\mathbb{R}}

\addto\captionsenglish{\DUTnames}

\begin{document}
\begin{DUTpreamble} % "DUT" because original preamble was clobbered.

%\begin{dedications}
%\Blindtext[3]
%\end{dedications}

%\begin{acknowledgments}
%\Blindtext[3]
%\end{acknowledgments}

\tableofcontents
\listoftables
\listoffigures

\begin{abstract}

Due to the increasing prevalence of falsified video content, it is important to be able to identify altered video. For certain types of video, removing small portions of content can change the perception of the events that transpire without leaving visually detectable evidence. Removing a set or sequence of frames from the beginning of a video can change the context of surrounding events, particularly in newsworthy content. Digital forensic techniques have been developed to detect this type of video manipulation, but were originally proposed for use on MPEG-2 video. Advances in video encoding, particularly in MPEG-4 and H.264 have potentially made these proposed techniques obsolete. In this thesis, we examine the performance of detectors built using the methodology from MPEG-2 applied to H.264 video, and show that indeed new methods are needed to detect frame deletion in modern video. We will propose a new method for extracting fingerprints left behind by frame deletion in H.264 as well as an expanded classification framework for ensuring robustness across videos captured by different camera models as well as variation in scene content or motion. We evaluate the performance of our proposed techniques as well as examine current limitations.

\end{abstract}
\end{DUTpreamble}

\begin{thesis}
\include{Introduction/introduction}
\include{Background/background}
\include{ProblemFormulation/problem_formulation}
\include{ProposedApproach/proposed_approach}
\include{ExperimentalResults/experimental_results}
\include{Conclusion/conclusion}
\end{thesis}

\printbibliography
%\bibliography{references}

%\appendix
%\include{example-a}

%\begin{vita}
%\Blindtext[3]
%\end{vita}

\end{document}
\endinput
%%
%% End of file `example.tex'.
